
GOD:  Thank you. 

I would like to thank Dr$.$ Steve Stevenson for the opportunity to 
pursue this research and paper.  Dr$.$ Stevenson's willingness to allow me 
freedom to explore various ideas made this experience a very beneficial 
one.  I'd also like to thank Dr$.$ Mike Westall for believing in me.
Without Dr$.$ Westall, this work would have never been realized. 
The paper and research in it's final form would not have been possible 
without the help of Dr$.$ Brian Malloy and Dr$.$ Sandee Hedetniemi.  I 
appreciate their advice and support. I'd also like to thank the computer
science professors that I was fortunate enough to work with while an undergrad
at Wofford College:  Dr$.$ Dan W$.$ Olds, Dr$.$ Angela Shiflet, Dr$.$ Ben Varn, and 
Dr$.$ Dan W$.$ Welch.  The four of you provided me with an excellent foundation 
in computing.  A special thanks to all of the 
undergraduates that have allowed me the opportunity to share my love of 
computer programming with them.  The many hours spent helping undergraduate 
computer science students in G-29 Jordan Hall will be one of my most 
cherished memories of my time at Clemson University. 
I'd be at fault if I did not give a great thanks to my friends and family.
My family has provided continued support throughout my educational career 
and for that I am forever indebted.  God has truly blessed me with a great 
family. Mom and Dad:  Thanks for all of the support! 
Mom: "I love Mooch, too!"   Dad: "Page me if you need something!"
A special thank you to my friends who kept me laughing via email 
when times were dark.  Thanks to all of my peers for allowing me to work
with the greatest minds in the computing world today.  Thanks to 
COMET3.CS.CLEMSON.EDU for allowing me to utilize her CPU cycles. 
Lastly, thanks go out to "Stone Cold" Steve Austin 
for showing me that hard-work, determination, and enthusiasm can make a 
world of difference.  And that's the bottom line...cause it's "Miller Time!"

