
\singlespace

As the networked computing environment continues to become more diverse, 
the need for interoperability among software and hardware components increases.
In recent years, several technologies have emerged in an attempt to solve this 
interoperability problem.  The Common Object Request Broker Architecture (CORBA)
from the Object Management Group (OMG) is one such technology.  CORBA developers
create a standard interface to a software component by specifying it's interface
in OMG's Interface Definition Language (IDL).   Based on this IDL specification,
components that may be implemented in different programming languages can 
interoperate with one another even if those components exist on different 
computing platforms. This is accomplished through the use of an Object Request 
Broker (ORB).  In order to implement a CORBA component in a particular programming
language, there must exist an ORB that supports language bindings for that 
programming language.   While most of the popular programming languages are well 
supported, some languages , like ML, go without CORBA support.   Since languages 
like ML often provide powerful capabilities in certain problem domains,  the 
ability to implement CORBA components in ML is highly desirable.  This paper 
presents one approach for providing CORBA capabilities to ML by interfacing with 
a freely available ORB with C language bindings called ORBit.  Through the use 
of a foreign function interface, ML can call C functions and vice-versa.  Using 
this ability, the C ORB Interface (CORBin) provides an IDL compiler, corbin-idl,  
which processes an IDL specification and generates C functions that utilize 
ORBit's functionality.  These functions are added to a library that is compiled 
into the ML runtime system.  This provides the ML programmer with the ability to  
communicate with other CORBA components and the ability to implement CORBA 
components in ML. Since instant messaging via the Internet has become popular, 
a case study is presented in which an instant messaging application utilizes a 
CORBA component implemented in ML.  

\doublespace
